\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/ms.tex
work on abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
    Large language models (LLMs) have found widespread interest as they can perform tasks they have not been explicitly been trained on. 
    This is relevant for the chemical sciences, which face the problem of learning from many small and diverse datasets that are frequently in the form of text.
    Thus, chemists have started to adapt LLMs to make predictions, optimize reactions, or even autonomously design and perform experiments.

    However, we still have only very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    In this work, we report an automatic framework, chembench, that we used to probe the chemical capabilities of LLMs compared to human chemists.

    % Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge
    We curated more than 6000 question answer pairs about a wide array of subfields, evaluated leading models such as GPT-4, and found that the best models, on average, outperform the best human chemists in our study. 
    The models, however, struggle with some chemical reasoning tasks that are easy for human experts and give overconfident misleading predictions, e.g. about the safety profile of chemicals.

    % One or two sentences to put the results into a more general context.

\end{abstract}
